\chapter*{List of Publications}
\addcontentsline{toc}{chapter}{List of Publications}
\setheader{List of Publications}
\label{publications}

%% We use the 'etaremune' environment (the reverse of 'enumerate') to get a
%% numbered list of publications in reverse chronological order. If the list of
%% authors is long, it might be useful to emphasize your own name with \textbf.
\Large{\textbf{Refereed publications}}

\begin{enumerate}\small{
\item \textbf{Z.\ Hou},  M. Nikolic, P. Benitez, and F. Bociort, "SMS2D designs as starting points for lens optimization," \href{https://doi.org/10.1364/OE.26.032463}{\textit{Opt. Express} \textbf{26}, 32463-32474 (2018)}.
\item \textbf{Z.\ Hou}, I. Livshits, and F. Bociort, "One-dimensional searches for finding new lens design solutions efficiently," \href{https://doi.org/10.1364/AO.55.010449}{\textit{Appl. Opt.} \textbf{55}, 10449-10456 (2016)}. 
\item A. Reyes-Reyes, \textbf{Z.\ Hou}, E. van Mastrigt, R. C. Horsten, J. C. de Jongste, M. W. Pijnenburg, H. P. Urbach, and N. Bhattacharya, "Multicomponent gas analysis using broadband quantum cascade laser spectroscopy," \href{https://doi.org/10.1364/OE.22.018299}{\textit{Opt. Express} \textbf{22}, 18299-18309 (2014)}.
}\end{enumerate}

\vspace{3mm}
\noindent
\Large{\textbf{Conference proceedings}}
\begin{enumerate}\small{
\item \textbf{Z.\ Hou},  I. Livshits, and F. Bociort, "Practical use of saddle-point construction in lens design," \href{https://doi.org/10.1117/12.2312494}{\textit{Proc. SPIE} \textbf{10690}, Optical Design and Engineering VII, 1069007 (2018)}.
\item \textbf{Z.\ Hou} and F. Bociort, "Reducible complexity in lens design," \href{https://doi.org/10.1117/12.2191364}{\textit{Proc. SPIE} \textbf{9626}, Optical Systems Design 2015: Optical Design and Engineering VI, 96260J (2015)}.
\item I. Livshits, \textbf{Z. Hou}, P. van Grol, Y. Shao, M. van Turnhout, P. Urbach, and F. Bociort, "Using saddle points for challenging optical design tasks," \href{https://doi.org/10.1117/12.2061975}{\textit{Proc. SPIE} \textbf{9192}, Current Developments in Lens Design and Optical Engineering XV, 919204 (2014)}.

}\end{enumerate}

\vspace{3mm}
\noindent
\Large{\textbf{Conference contributions}}
\begin{enumerate}\small{
\item \textbf{Z. Hou}, Y. Zhang, and F. Bociort, "Design Using Saddle Point Construction in Complex Lens Systems," oral presentation at the European Optical Society Biennial Meeting, Delft, the Netherlands (October 2018).
\item \textbf{Z. Hou}, I. Livshits, and F. Bociort, "Practical use of saddle-point construction in lens design," oral presentation at the SPIE Optical Systems Design conference, Frankfurt, Germany (May 2018).
\item \textbf{Z. Hou}, "One-dimensional searches for finding new lens design solutions efficiently,"  Excellent Oral Presentation Award at the International Doctoral Students Conference on "Opportunities and Challenges Arises from Global Technological Revolution", Zhejiang, China (May 2017).
\item \textbf{Z. Hou}, F. Bociort, I. Livshits, and H.P. Urbach, "A systematic study on the design landscape of a pin-hole lens," oral presentation at the 10th International Conference on Optics-photonics Design and Fabrication, Weingarten, Germany  (March 2016).
\item \textbf{Z. Hou}, F. Bociort, and I. Livshits, "Reducible complexity in lens design - 
replacing high-dimensional search by one-dimensional searches to find new solutions efficiently," poster presentation at the IST Science Day, Delft, the Netherlands (October 2015).
\textbf{Z. Hou} and F. Bociort, "Reducible complexity in lens design," invited Paper at the SPIE Optical Systems Design conference, Jena, Germany (September 2015). 
\item F. Bociort, P. van Grol, I. Livshits, \textbf{Z. Hou}, Y. Shao, P. Urbach, "Saddle-point methods for systematic design," the European Optical Society Biennial Meeting, Berlin Adlershof, Germany (September 2014).
I. Livshits, \textbf{Z. Hou}, P. van Grol, Y. Shao, M. van Turnhout, P. Urbach, and F. Bociort, "Using saddle points for challenging optical design tasks," the SPIE OPTICAL ENGINEERING + APPLICATIONS conference, San Diego, U.S.A. (August 2014).

}\end{enumerate}
